\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Moch. \underline{Nafkhan} Alzamzami} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{(+62) 85815805174 \\ Bandung, Indonesia}
\address{\href{mailto:nafkhanalzamzami@gmail.com}{nafkhanalzamzami@gmail.com} \\ \href{https://www.linkedin.com/in/nafkhanzam/}{linkedin.com/in/nafkhanzam/} \\ \href{www.nafkhanzam.com}{www.nafkhanzam.com}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

% {Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.}
{A computer scientist with 4+ years of experience in software engineering and machine learning.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Computer Science}, Institut Teknologi Bandung \hfill {Expected 2023}\\
Relevant Coursework: Deep Learning, Natural Language Processing.\\
Current GPA: 3.92 / 4.00

{\bf Bachelor of Computer Science}, Institut Teknologi Bandung \hfill {2018 - 2022}\\
GPA: 3.74 / 4.00
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Backend Development, Machine Learning Researcher.
\\
Soft Skills & Tech Lead.\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer} \hfill Feb 2022 - Apr 2022\\
Nubela

\textbf{Site Reliability Engineer Intern} \hfill May 2021 - Aug 2021\\
Shopee Indonesia
\begin{itemize}
  \itemsep -3pt {}
  \item Managed to prevent unnoticed soon-to-expire SSL by creating an email notifier and a dashboard.
  \item Managed to reduce the cloud server costs by implementing a scheduler for scaling Kubernetes deployments.
\end{itemize}

% \textbf{Tech Lead} \hfill Jan 2021 - May 2022\\
% pesanpesta
% \begin{itemize}
%   \itemsep -3pt {}
%   \item Made executive decisions on behalf of the company's technological requirements.
%   \item Developed an e-commerce website application with complex features.
%   \item Implemented everything in object-oriented, domain-driven design, SOLID principles, and DRY principles.
% \end{itemize}

% \textbf{Tech Lead} \hfill Jun 2020 - Dec 2020\\
% AlinaMed
% \begin{itemize}
%   \itemsep -3pt {}
%   \item Made executive decisions on behalf of the company's technological requirements.
%   \item Lead the backend and frontend teams.
%   \item Developed a homecare and telemedicine backend and mobile app.
%   \item Maintained a tracker system for clinics keeping track of their covid patients.
% \end{itemize}

\textbf{Software Development Engineer Intern} \hfill Jun 2020 - Aug 2020\\
GDP Labs
\begin{itemize}
  \itemsep -3pt {}
  \item Researched OpenAPI 3 with the integrations using Java Spring Frameworks.
  \item Researched FaunaDB with GraphQL and FQL.
\end{itemize}

\textbf{Backend Developer} \hfill Aug 2019 - Feb 2020\\
Xtremax
\begin{itemize}
  \itemsep -3pt {}
  \item Developed a web application using ASP.Net.
  \item Researched about serving generated static sites using CI/CD.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PUBLICATIONS}
\begin{itemize}
  \item \textbf{M. N. Alzamzami} and F. N. Azizah, "GraphQL-based Backend Service Development Tool for CRUD Operations, Authentication, and Authorization," 2022 International Conference on Data and Software Engineering (ICoDSE), 2022, pp. 77-82, doi: 10.1109/ICoDSE56892.2022.9971818.
\end{itemize}
\end{rSection}


\begin{rSection}{ACHIEVEMENTS}
\begin{itemize}
  \item \textbf{IEEEXtreme 13.0} \hfill 2019\\Ranked 26th out of 2,781 teams
  \item \textbf{ARKAVIDIA 5.0 COMPETITIVE PROGRAMMING} \hfill 2019\\Finalist
  \item \textbf{INTERNATIONAL COLLEGIATE PROGRAMMING CONTEST} \hfill 2018\\Regional Finalist
\end{itemize}
\end{rSection}

\end{document}
